---
title: "Group 1: Multivariate analysis of australian climate data"
author:  "Andrea Iglesias Munilla, Kathryn Weissman, Diana Galindo Gonz치lez, Mateo J치come Gonz치lez y Pedro Gonz치lez Prado"
date: "`r Sys.Date()`"
output:
   html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: true
---

## Results {.tabset}

```{r setup, include=FALSE, results='hide'}
#INSTALL & LOAD LIBRARIES
# Required packages
pkgs<-c('rstudioapi','flexdashboard','tidyverse','DT','naniar','tidyr','sf','ggplot2','cowplot', 'googleway', 'ggrepel', 'VIM','ggspatial', 'libwgeom', 'sf', 'rnaturalearth','rnaturalearthdata','gridExtra','grid','lattice','FactoMineR','factoextra','corplot','heatmaply','ade4','corrplot')

# Non-installed packages
inspkgs<-pkgs[!pkgs %in% installed.packages()]
for(libs in inspkgs) install.packages(libs,repos = "http://cran.us.r-project.org")

# Loading required
sapply(pkgs,require,character=TRUE)


```


```{r settings, include=FALSE, results='hide'}

# CLEARING ENVIRONMENT #

rm(list=ls(all=TRUE))

#PREPARE WORK DIRECTORY AND IMPORT DATASET

current_path <- getActiveDocumentContext()$path 
setwd(dirname(current_path ))

df <- read.csv('weatherAUSOriginal.csv', stringsAsFactors = T)
```

This project seeks to develop, train and evaluate a statistical model that helps end-users make predictions about whether or not there will be rainfall the following day, given the weather conditions on a given day in Australia. In addition, several multivariate techniques will be implemented in order to extract key insights and relevant information from the available historical data. A better understanding of the factors influencing rainfall in Australia and how these may have changed over time given the harsh climate changes the territory has experienced in the last decade may be of use to predict future droughts and wildfire crises. 

The main data set was obtained from the repository at [Kaggle.com][1]. This data set is built using publicly available climate data, provided by the [Australian Bureau of Meteorology][2] and measured by weather stations distributed across the country. It contains more than 100,000 daily weather observations over a 10-year period from 2007 to 2017 from 49 unique locations in Australia. These observations include temperature, rainfall, atmospheric pressure, evaporation, humidity, wind direction, and wind speed at different times during the day.  More specifically, the dataset contains 24 columns in total. Columns 1 through 21 are defined by the [Australian Government Bureau of Meteorology][2]:


1. **Date**: date of the observation. 
2. **Location**: common name for the weather station location. 
3. **MinTemp**: minimum temperature in the 24 hours to 9am, degrees Celsius.
4. **MaxTemp**: maximum temperature in the 24 hours from 9am, degrees Celsius.
5. **Rainfall**: rainfall in the 24 hours to 9am, millimeters. 
6. **Evaporation**: 'Class A' pan evaporation in the 24 hours to 9am, millimeters.
7. **Sunshine**: number of hours of bright sunshine in the 24 hours to midnight.
8. **WindGustDir**: direction of the strongest wind gust in the 24 hours to midnight, 
measured with 16 compass points.  
9. **WindGustSpeed**: speed of strongest wind gust in the 24 hours to midnight, km/h.
10. **WindDir9am**: wind direction  at 9am, measured with 16 compass points. 
11. **WindDir3pm**: wind direction at 3pm, measured with 16 compass points. 
12. **WindSpeed9am**: average wind speed over the 10-minute period prior to 9am, km/h.
13. **WindSpeed3pm**: average wind speed over the 10-minute period prior to 3pm, km/h.
14. **Humidity9am**: relative humidity percentage at 9am. 
15. **Humidity3pm**: relative humidity percentage at 3pm.
16. **Pressure9am**:  atmospheric pressure (hpa) reduced to mean sea level at 9am.
17. **Pressure3pm**: atmospheric pressure (hpa) reduced to mean sea level at 3pm.
18. **Cloud9am**: fraction of sky obscured by cloud at 9am, measured in oktas, a unit of eights that describes the amount of cloud cover at any given location such as a weather station, ranging from 0 (completely clear sky) to 8 (completely covered sky). Value 9 (sky obstructed from view) https://en.wikipedia.org/wiki/Okta 
19. **Cloud3pm**: fraction of sky obscured by cloud at 3pm, measured in oktas.
20. **Temp9am**: temperature at 9am, measured in degree celsius. 
21. **Temp3pm**: temperature at 3pm, measured in degree celsius.
22. **RainToday**: boolean variable; Yes if precipitation (mm) in the 24 hours to 9am exceeds 1 mm, otherwise No. 
23. **RainTomorrow**: boolean variable; Yes if the following day precipitation exceeds 1 mm, otherwise no. 


